%----------------------------------------------------------------------------------------
%	Projects
%----------------------------------------------------------------------------------------
\vspace{\sectionpadding}
\cvsect{Projects}
\entry
    {Indoor Air Quality Controller}
    {\quad \href{https://github.com/donovanclay/isy}{https://github.com/donovanclay/isy}}
    {Jul. 2022 - Sep. 2023}
    {
        This controller manages the supply and exhaust fans in a house to keep stable air pressure and humidity.
        \begin{condenseditemize}
            \item Communicated with APIs to poll local weather, air quality, and the house's security system

            \item Used sensors to detect airflow, humidity, motion, and occupancy and control fans based on that data
            
            \item Used Python sockets to implement a Websocket to send live updates about the state of the application
            
            \item Used React and NextJS to develop and Docker to deploy a local website to show real time diagnostic data
            
            \item Used Python to implement logic to equalize exhaust airflow with supply airflow
        \end{condenseditemize}
    }

\entry
    {\href{https://github.com/donovanclay/foodbot}{``Foodbot'' Discord Bot}}
    {\quad \href{https://github.com/donovanclay/foodbot}{https://github.com/donovanclay/foodbot}}
    {Jan. 2023 - May 2023}
    {
        This is a general purpose Discord bot with many fun, random features. It can check when UW CS homework is released, generate images, chat with the user with different personalities, and track keyword occurrences and typos.
        
        APIs used: ChatGPT, Bing Spell Check, Stability AI Image Generation.
        \begin{condenseditemize}
            \item Harnesses APIs for features like typo recognition, prompt based image generation, and a chat bot with configurable personalities

            \item Uses REST to poll UW CSE course websites to download homework
        \end{condenseditemize}
    }

\entry
    {\href{https://devpost.com/software/illustraitor}{illustrAItor}}
    {Finalist in UW Hackathon 2022 \quad\href{https://github.com/donovanclay/illustrAItor}{https://github.com/donovanclay/illustrAItor}}
    {Oct. 2022}
    {
        This project makes reading more enjoyable by complementing it with customizable AI-generated illustrations. illustrAItor creates captivating illustrations to complement the passage of text being read.\\
        APIs used: Stability AI Image Generation, Google Books.
        \begin{condenseditemize}
            \item Produced the project in 24 hours in a highly competitive environment
            \item Worked in a small group of 4 for long hours
            \item Used multiple API's to pull and serve information to and from different services
        \end{condenseditemize}
    }
    